A Test of the Frequency Independence Assumption of the Power System Parameters used in Geomagnetically Induced Current Calculations

### 2019-02-11 paper.tex
update figs

\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{figures/plot_model_summaryTF_aves_SN-options-1.pdf}
\caption{Signal-to-noise ratios at the evaluation frequencies for the four models.}
\label{SN}
\end{figure}

\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{figures/plot_model_summaryTF_aves_aobo_histograms-options-1.pdf}
\caption{Distribution of parameters in Model 1. Each set of parameters were computed 35 times using one day of 1-second cadence data. The circle/dot on the horizontal axis indicates the average of each histogram: $a_o$ = 71.9 A/(V/km) and $b_o$ = -70.0 A/(V/km).}
\label{histogram}
\end{figure}

\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{figures/plot_model_summaryTF_aves_H-options-1.pdf}
\caption{Impulse responses for Models 1, 2, and 4. The circles at $t = 0$ correspond to the impulse response for Model 1; the red/blue lines are the impulse responses for Model 2 and 4. The values of $a_o$ and $b_o$ have been scaled by a factor of 10 for readability.}
\label{H}
\end{figure}

\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{figures/plot_model_summaryTF_aves_Z-options-1.pdf}
\caption{Frequency domain transfer functions for Models 1-3, 2, and 4. By definition, the frequency domain transfer functions for $A_o$ and $B_o$ are constant and equal to $a_o$ and $b_o$.}
\label{Z}
\end{figure}

>>>>

\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{figures/plot_model_summary_SN-options-1.pdf}
\caption{Signal-to-noise ratios at the evaluation frequencies for the four models.}
\label{SN}
\end{figure}

\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{figures/plot_model_summary_aobo_histograms-options-1.pdf}
\caption{Distribution of parameters in Model 1. Each set of parameters were computed 35 times using one day of 1-second cadence data. The circle/dot on the horizontal axis indicates the average of each histogram: $a_o$ = 71.9 A/(V/km) and $b_o$ = -70.0 A/(V/km).}
\label{histogram}
\end{figure}

\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{figures/plot_model_summary_H-options-1.pdf}
\caption{Impulse responses for Models 1, 2, and 4. The circles at $t = 0$ correspond to the impulse response for Model 1; the red/blue lines are the impulse responses for Model 2 and 4. The values of $a_o$ and $b_o$ have been scaled by a factor of 10 for readability.}
\label{H}
\end{figure}

\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{figures/plot_model_summary_Z-options-1.pdf}
\caption{Frequency domain transfer functions for Models 1-3, 2, and 4. By definition, the frequency domain transfer functions for $A_o$ and $B_o$ are constant and equal to $a_o$ and $b_o$.}
\label{Z}
\end{figure}
